Demystifying the Combination of Dynamic Slicing and \\ Spectrum-based Fault Localization

### 2019-02-25 paper/ijcai/paper.tex
cleaning variants

To analyze the impact of dynamic slicing in context, we also compared
\combpar{k} and \sfl{}$^{k}$ considering the number of cases where the
fault is captured by the technique within a certain bound $k$. Note
that the reason \sfl{}$^{k}$ misses the fault is different compared to
\combpar{k}. \sfl{}$^{k}$ captures the fault if it is included within
the top $k$ files; it misses the fault
otherwise. Table~\ref{table:fsws} shows results, indicating that
\combpar{k}, typically, captures more faults compared to
\sfl{}$^{k}$. In only two cases, highlighted in gray color,
\sfl{}$^{k}$ outperformed \combpar{k}. These results show that the
majority of faulty statements are found on the $5$ highest ranked
faulty classes and that \combpar{10} is the variant of our approach
that performs better, missing only $23$ out of the
\numFaults\ ($\sim$8.8\%) faults.

@@

Table \ref{table:st}
presents the statistics to determine if the observed results are
statistically significant. Shapiro-Wilk tests the null hypothesis that
results are drawn from a normal distribution. The test is perfomed for
all techniques and its variants. With $99\%$ of confidence, the
results tell us that the distributions are not normal. Given that $C$
is not normally distributed, we use Friedman test, a non-parametric
statistical test of hypothesis. The null hypothesis is that the
ranking results of all techniques and variants are the same. With
$99\%$ confidence, the results show that the distributions are
distinct. To understand which techniques perform differently, \ie{} to answer
the question \textit{Does \combpar{k} perform differently than
\sfl{}$^{k}$}, we performed a Siegel post-hoc analysis. Figure
\ref{fig:performance} reports the results of Siegel analysis for all
pairs of techniques. Each square represents the
statistical significance of the diagnostic accuracy amongst the different
techniques, i.e., if it is significant it means that the techniques perform
differently. We can determine with $95\%$ confidence that the
performance of each pair of techniques is different.

>>>>

To analyze the impact of dynamic slicing in context, we also compared
\combpar{k} and \sfl{}$^{k}$ considering the number of cases where the
fault is captured by the technique within a certain bound $k$. Note
that the reason \sfl{}$^{k}$ misses the fault is different compared to
\combpar{k}. \sfl{}$^{k}$ captures the fault if it is included within
the top $k$ files; it misses the fault
otherwise. Table~\ref{table:fsws} shows results, indicating that
\combpar{k}, typically, captures more faults compared to
\sfl{}$^{k}$. In only two cases, highlighted in gray color,
\sfl{}$^{k}$ outperformed \combpar{k}. These results show that the
majority of faulty statements are found on the $5$ highest ranked
faulty classes and that \combpar{10} is the technique
that performs better, missing only $23$ out of the
\numFaults\ ($\sim$8.8\%) faults.

@@

Table \ref{table:st}
presents the statistics to determine if the observed results are
statistically significant. Shapiro-Wilk tests the null hypothesis that
results are drawn from a normal distribution. The test is perfomed for
all techniques and both $k$s. With $99\%$ of confidence, the
results tell us that the distributions are not normal. Given that $C$
is not normally distributed, we use Friedman test, a non-parametric
statistical test of hypothesis. The null hypothesis is that the
ranking results of all techniques for each $k$ are the same. With
$99\%$ confidence, the results show that the distributions are
distinct. To understand which techniques perform differently, \ie{} to answer
the question \textit{Does \combpar{k} perform differently than
\sfl{}$^{k}$}, we performed a Siegel post-hoc analysis. Figure
\ref{fig:performance} reports the results of Siegel analysis for all
pairs of techniques. Each square represents the
statistical significance of the diagnostic accuracy amongst the different
techniques, i.e., if it is significant it means that the techniques perform
differently. We can determine with $95\%$ confidence that the
performance of each pair of techniques is different.
